Coronal Fourier power spectra: implications for coronal seismology and coronal heating.

### 2014-06-18 tex/paper1/paper1.tex
edits to the paper

Secondly, since each loop is different, and the reaction of the
coronal plasma to an energy deposition event is a highly nonlinear
function of the coronal conditions it occurs in,

  It is known that

Secondly, the energy radiated as a function of the energy deposited in
each event and the existing plasma properties must be consistently
modeled.  This is required to understand how much radiation at each
wavelength is emitted from the plasma.  This is a complex task to do
correctly, and there is much work ....

Finally, the AIA instrument
filters the emitted radiation, and this too must be modeled in order
to understand the observed \Fps.  These three features must be modeled
in order to test the hypothesis that ubiquitous energy deposition
events are the root cause of the observed power-law like behavior of
the Fourier power spectra.

There has been a considerable amount of work in modeling the
AIA-detected plasma response...  \cite{}

>>>>

Secondly, the amount of energy and the wavelengths at which it is
radiated is a highly nonlinear function of the energy deposited in
each event, depending on the existing plasma properties and the
location of the energy deposition in the loop structure.  This must
all be consistently modeled on each loop and summed over multple loops
to mimic the line-of-sight effects, as noted above.

Much effort has
been \cite{???} EBTEL.

EBTEL , O'Dwyer paper???

Finally, the AIA instrument filter response must also be understood
and modeled in in order to understand which emission lines contribute
to the final observed image, and ultimately the \Fps\ for each
region.  The AIA filter response has been studied by
\cite{2010AA...521A..21O}
